Commit Rater

### 2015-08-26 presentations/paper/methodology.tex
Remove lowbobiness
Make sum over elements readable
Add machine learning info in Commit-level section

\subsubsection{Commit-level}
\label{subs:Commit-level}
Although looking at the results of a single commit might be interesting for debugging the criteria tests, there are not many options for analysis. The percentage of passed tests could serve as a rating for the commit, where 100\% means having passed all tests, but no further conclusions could be drawn from this level. Therefore, we did not concern ourselves with this level.

@@

\begin{equation}
  \label{eq:weightedAverage}
  wa(triples) = \frac{1}{|triples|} \times \sum{t \element triples} rate(t) \times weight(t)
\end{equation}

>>>>

\subsubsection{Commit-level}
\label{subs:Commit-level}
Commit-level results, i.e. which criteria a single commit does or does not fulfill, is used for the machine learning aspect of this paper. Each commit represents a data set of boolean values. Due to the ways each criterion is formulated, true values are always good. For simplicity's sake, undefined values are considered bad and result in a false value.

See section \ref{sec:results2} for a detailed explanation of our machine learning process.

@@

\begin{equation}
  \label{eq:weightedAverage}
  wa(triples) = \frac{1}{|triples|} \times \sum\nolimits_{t \in triples} rate(t) \times weight(t)
\end{equation}
